---
title: "Case_Study_Group_14"
output: html_document
---test---branch--

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r, echo = FALSE}

library(tidyverse)

library(knitr)

library(readxl)

library(data.table)

library(tidyr)
```

##import data for components
```{r}

```{r}
library(readr)
```




```{r}

Einzelteil17 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T17.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

```


```{r}
Einzelteil4 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T04.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)
Einzelteil4$Fehlerhaft_Datum<-as.Date(Einzelteil4$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil4$origin<-as.Date(Einzelteil4$origin,format = "%d-%m-%Y")
Einzelteil4 <- transform(Einzelteil4, Produktionsdatum = Einzelteil4$Produktionsdatum_Origin_01011970 + Einzelteil4$origin)
Einzelteil4 <- Einzelteil4[,-(9:10),drop=FALSE]
```

```{r}
Einzelteil5<-read_csv("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T05.csv)%>% select(-X1, -X1_1)%>% select(1,3,4,5,6,7,2)%>% rename(ID_T05=ID_T05.x,Herstellernummer=Herstellernummer.x,Werksnummer=Werksnummer.x,Fehlerhaft=Fehlerhaft.x,Fehlerhaft_Datum=Fehlerhaft_Datum.x,Fehlerhaft_Fahrleistung=Fehlerhaft_Fahrleistung.x,Produktionsdatum=Produktionsdatum.x)
Einzelteil5<-Einzelteil5[!is.na(Einzelteil5$ID_T05),]
```

```{r}
Einzelteil6 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T06.csv", header=TRUE, stringsAsFactors = FALSE)
Einzelteil6$Fehlerhaft_Datum<-as.Date(Einzelteil6$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil6$origin<-as.Date(Einzelteil6$origin,format = "%d-%m-%Y")
Einzelteil6 <- transform(Einzelteil6, Produktionsdatum = Einzelteil6$Produktionsdatum_Origin_01011970 + Einzelteil6$origin)
Einzelteil6 <- Einzelteil6[,-(9:10),drop=FALSE]
```

```{r}
Einzelteil8 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T08.csv", header=TRUE, stringsAsFactors = FALSE)
Einzelteil8$Fehlerhaft_Datum<-as.Date(Einzelteil8$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil8$origin<-as.Date(Einzelteil8$origin,format = "%d-%m-%Y")
Einzelteil8 <- transform(Einzelteil8, Produktionsdatum = Einzelteil8$Produktionsdatum_Origin_01011970 + Einzelteil8$origin)
Einzelteil8 <- Einzelteil8[,-(9:10),drop=FALSE]
```

```{r}
Einzelteil10 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T10.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)
Einzelteil10$Fehlerhaft_Datum<-as.Date(Einzelteil10$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil10$origin<-as.Date(Einzelteil10$origin,format = "%d-%m-%Y")
Einzelteil10 <- transform(Einzelteil10, Produktionsdatum = Einzelteil10$Produktionsdatum_Origin_01011970 + Einzelteil10$origin)
Einzelteil10 <- Einzelteil10[,-(9:10),drop=FALSE]
```

```{r}
Einzelteil12 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T12.csv", header=TRUE, sep = ";", stringsAsFactors = FALSE)
```


```{r}
Einzelteil13 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T13.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)
Einzelteil13$Fehlerhaft_Datum<-as.Date(Einzelteil13$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil13$origin<-as.Date(Einzelteil13$origin,format = "%d-%m-%Y")
Einzelteil13 <- transform(Einzelteil13, Produktionsdatum = Einzelteil13$Produktionsdatum_Origin_01011970 + Einzelteil13$origin)
Einzelteil13 <- Einzelteil13[,-(9:10),drop=FALSE]
```

```{r}
Einzelteil14 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T14.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)
Einzelteil14$Fehlerhaft_Datum<-as.Date(Einzelteil14$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil14$origin<-as.Date(Einzelteil14$origin,format = "%d-%m-%Y")
Einzelteil14 <- transform(Einzelteil14, Produktionsdatum = Einzelteil14$Produktionsdatum_Origin_01011970 + Einzelteil14$origin)
Einzelteil14 <- Einzelteil14[,-(9:10),drop=FALSE]
```

```{r}
Einzelteil18 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T18.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)
Einzelteil18$Fehlerhaft_Datum<-as.Date(Einzelteil18$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil18$origin<-as.Date(Einzelteil18$origin,format = "%d-%m-%Y")
Einzelteil18 <- transform(Einzelteil18, Produktionsdatum = Einzelteil18$Produktionsdatum_Origin_01011970 + Einzelteil18$origin)
Einzelteil18 <- Einzelteil18[,-(9:10),drop=FALSE]
```


```{r}
Einzelteil19 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T19.csv", header=TRUE, sep=",", stringsAsFactors = FALSE)
Einzelteil19$Fehlerhaft_Datum<-as.Date(Einzelteil19$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil19$origin<-as.Date(Einzelteil19$origin,format = "%d-%m-%Y")
Einzelteil19$origin<-as.Date(Einzelteil19$origin,format = "%d-%m-%Y")
Einzelteil19 <- transform(Einzelteil19, Produktionsdatum = Einzelteil19$Produktionsdatum_Origin_01011970 + Einzelteil19$origin)
Einzelteil19 <- Einzelteil19[,-(9:10),drop=FALSE]
```


```{r}
Einzelteil15 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T15.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)
Einzelteil15 <- unite(Einzelteil15, Produktionsdatum,Produktionsdatum.x, Produktionsdatum.y, sep = "_", remove = TRUE)
Einzelteil15 <- unite(Einzelteil15, Herstellernummer,Herstellernummer.x, Herstellernummer.y, sep = "_", remove = TRUE)
Einzelteil15 <- unite(Einzelteil15, Werksnummer,Werksnummer.x, Werksnummer.y, sep = "_", remove = TRUE)
Einzelteil15 <- unite(Einzelteil15, Fehlerhaft,Fehlerhaft.x, Fehlerhaft.y, sep = "_", remove = TRUE)
Einzelteil15 <- unite(Einzelteil15, Fehlerhaft_Datum,Fehlerhaft_Datum.x, Fehlerhaft_Datum.y, sep = "_", remove = TRUE)
Einzelteil15 <- unite(Einzelteil15, ID_T15,ID_T15.x, ID_T15.y, sep = "_", remove = TRUE)
Einzelteil15 <- unite(Einzelteil15, Fehlerhaft_Fahrleistung,Fehlerhaft_Fahrleistung.x, Fehlerhaft_Fahrleistung.y, sep = "_", remove = TRUE)
```




--------------------- TXT FILES --------------------------------------------------
```{r}
Einzelteil9<-read_file("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T09.txt")
Einzelteil9<-str_split(Einzelteil9,pattern="\\\"[0-9]+\"\\\\[0-9]+\\\\\\\"")
Einzelteil9 <- data.frame(Einzelteil9)
Einzelteil9<-separate(Einzelteil9,col=1,sep = "\\\\",into=c("ID_T35","Produktionsdatum","Herstellernummer","Werksnummer","Fehlerhaft","Fehlerhaft_Datum","Fehlerhaft_Fahrleistung"))
Einzelteil9 <- Einzelteil9[-1,]
Einzelteil9$Herstellernummer <- str_remove_all(Einzelteil9$Herstellernummer,"\"")
Einzelteil9$ID_T35 <- str_remove_all(Einzelteil9$ID_T35,"\"")
Einzelteil9$Fehlerhaft_Datum<-as.Date(Einzelteil9$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil9$Produktionsdatum<-as.Date(Einzelteil9$Produktionsdatum,format = "%Y-%m-%d")
Einzelteil9<-select(Einzelteil9,1,3,4,5,6,7,2)
Einzelteil9[,c(2,3,4,6)]<-sapply(Einzelteil9[,c(2,3,4,6)],as.numeric)
```

```{r}
Einzelteil7<-read_file("F:/Downloads/Data/Einzelteil/Einzelteil_T07.txt")
Einzelteil7<-str_split(Einzelteil7,pattern="\"[0-9]+\"\t[0-9]+\t\"")
Einzelteil7 <- data.frame(Einzelteil7)
Einzelteil7<-separate(Einzelteil7,col=1,sep = "\t",into=c("ID_T07","Produktionsdatum","Herstellernummer","Werksnummer","Fehlerhaft","Fehlerhaft_Datum","Fehlerhaft_Fahrleistung"))
Einzelteil7<- Einzelteil7[-1,]
Einzelteil7<-select(Einzelteil7,1,3,4,5,6,7,2)
Einzelteil7$Herstellernummer <- str_remove_all(Einzelteil7$Herstellernummer,"\"")
Einzelteil7$ID_T07 <- str_remove_all(Einzelteil7$ID_T07,"\"")
Einzelteil7$Fehlerhaft_Datum<-as.Date(Einzelteil7$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil7$Produktionsdatum<-as.Date(Einzelteil7$Produktionsdatum,format = "%Y-%m-%d")
Einzelteil7[,c(2,3,4,6)]<-sapply(Einzelteil7[,c(2,3,4,6)],as.numeric)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
