---
title: "Case_Study_Group_14"
output: html_document
---test---branch--

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r, echo = FALSE}

library(tidyverse)

library(knitr)

library(readxl)

library(data.table)

library(tidyr)
```

##import data for components
```{r}

```{r}
library(readr)
```


```{r}
Einzelteil4 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T04.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

Einzelteil5 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T05.csv", header=TRUE, sep=",", stringsAsFactors = FALSE)

Einzelteil6 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T06.csv", header=TRUE, stringsAsFactors = FALSE)

Einzelteil8 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T08.csv", header=TRUE, stringsAsFactors = FALSE)

Einzelteil10 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T10.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

Einzelteil12 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T12.csv", header=TRUE, sep = ";", stringsAsFactors = FALSE)

Einzelteil13 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T13.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

Einzelteil14 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T14.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

Einzelteil15 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T15.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

Einzelteil17 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T17.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

Einzelteil18 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T18.csv", header=TRUE, sep=";", stringsAsFactors = FALSE)

Einzelteil19 <- fread("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T19.csv", header=TRUE, sep=",", stringsAsFactors = FALSE)
```


```{r}
Einzelteil9<-read_file("~/Desktop/IDA 2019/Shared/Data/Einzelteil/Einzelteil_T09.txt")
Einzelteil9<-str_split(Einzelteil9,pattern="\\\"[0-9]+\"\\\\[0-9]+\\\\\\\"")
Einzelteil9 <- data.frame(Einzelteil9)
Einzelteil9<-separate(Einzelteil9,col=1,sep = "\\\\",into=c("ID_T35","Produktionsdatum","Herstellernummer","Werksnummer","Fehlerhaft","Fehlerhaft_Datum","Fehlerhaft_Fahrleistung"))
Einzelteil9 <- Einzelteil9[-1,]
Einzelteil9$Herstellernummer <- str_remove_all(Einzelteil9$Herstellernummer,"\"")
Einzelteil9$ID_T35 <- str_remove_all(Einzelteil9$ID_T35,"\"")
Einzelteil9$Fehlerhaft_Datum<-as.Date(Einzelteil9$Fehlerhaft_Datum,format = "%Y-%m-%d")
Einzelteil9$Produktionsdatum<-as.Date(Einzelteil9$Produktionsdatum,format = "%Y-%m-%d")
Einzelteil9<-select(Einzelteil9,1,3,4,5,6,7,2)
Einzelteil9[,c(2,3,4,6)]<-sapply(Einzelteil9[,c(2,3,4,6)],as.numeric)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
